### 2020-06-05 writeup/experiments.tex
8 pages

We validate our theory and algorithmic insights.
First, we validate the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
We show that single-task learning results can help predict positive or negative transfer for both datasets.
Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
Third, when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
Finally, we validate our theoretical results on text classification tasks.

@@

\subsection{Experimental Setup}

@@

{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer with GloVe embeddings
followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

{\it ChestX-ray14:} This dataset contains 112,120 frontal-view X-ray images and each image has up to 14 diseases.
This is a 14-task multi-label image classification problem.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

@@

\subsection{Experimental Results}

@@

\subsection{Ablation Studies}

We validate our three theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.
In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
We select a pair of similar versus dissimilar task based on our domain knowledge or these tasks (cf. Appendix \ref{app_it} for the detailed procedure).
We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
In Figure \ref{fig_ab_data}, we validate the phenomenon that adding more source data samples does not always improve performance on the target task.
In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL performance.
We average the result over all 15 task pairs.
The result shows that as source samples increases, performing the alignment procedure shows a bigger improvement over MTL.
The experimental procedure is left to Appendix \ref{app_it}.

>>>>

\vspace{-0.05in}
We validate our theory and algorithmic insights.
First, we validate the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
We show that single-task learning results can help predict positive or negative transfer for both datasets.
Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
Third, when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
Finally, we validate our theoretical results on text classification tasks.

@@

\vspace{-0.07in}
\subsection{Experimental Setup}

@@

{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
The question is to predict positive or negative sentiment expressed in the text.
We use an embedding layer with GloVe embeddings
followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.

%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images.
There are 14 diseases (tasks) for every image that we would like to predict.
We use AlexNet as the shared module.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

@@

\vspace{-0.07in}
\subsection{Experimental Results}

@@

\vspace{-0.07in}
\subsection{Validating the Theoretical Results}

We validate our three theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.
In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
We select each task pair based on our domain knowledge.
We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
In Figure \ref{fig_ab_data}, we validate the phenomenon that adding more source data samples does not always improve performance on the target task.
In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL performance.
We average the results over all 15 task pairs.
The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
The rest of experimental procedures are left to Appendix \ref{app_it}.

### 2020-06-05 writeup/related.tex
8 pages

\section{Related Work}

We refer the interested readers to several excellent surveys on multi-task and transfer learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.

\textit{Multi-task learning theory.}
Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} Generalization bounds for linear separation settings of MTL
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines empirical and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their results do not apply to explain the phenomena of negative transfer.

% Adding a regularization over $B$, e.g. .
\textit{Multi-task learning methodology.}
Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
Argyriou et al. \cite{AEP08} presents a convex algorithm which learns common sparse representations across a pool of related tasks.
Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,R17}.
We believe that the technical tools we have developed can also be applied to many other multi-task learning models.

@@

\section{Conclusions and Discussions}

>>>>

\vspace{-0.05in}
\section{Related Work}
\vspace{-0.05in}

We refer the interested readers to several excellent surveys on multi-task  learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
Below, we describe several lines of work that are most related to this work.

\textit{Multi-task learning theory.}
Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} Generalization bounds for linear separation settings of MTL
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines empirical and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques do not explain the phenomena of negative transfer.

% Adding a regularization over $B$, e.g. .
\textit{Multi-task learning methodology.}
Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
Argyriou et al. \cite{AEP08} presents a convex algorithm which learns common sparse representations across a pool of related tasks.
Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,KD12,R17}.
We believe that the technical tools we have developed can also be applied to many other multi-task learning models.

@@

\vspace{-0.05in}
\section{Conclusions and Open Problems}
\vspace{-0.05in}

In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
We provided tight concentration bounds for the bias and the variance.
Based on these bounds, we analyzed the impact of three properties, including task similarity, sample data and covariate shift on the bias and variance, to derive conditions for transfer.
%Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
We validated our theoretical results.
Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging result inspired by our theory.
We describe several open questions for future work.
First, our bound on the bias term (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
Tightening this error bound can potentially cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
Second, it would be interesting to extend our results to non-linear settings.
We remark that this likely requires addressing significant technical challenges in order to deal with non-linearity.
